Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-12-19 supplement.tex
finish filling in table S7

>>>>

\begin{table}[ht]
    \caption{
        \label{tab:supp-confidence-intervals}
        \textbf{GIM-computed confidence intervals are not underestimated.}
        CIs computed with the Godambe information matrix (GIM) are largely
        similar (i.e., within an order of magnitude) to those estimated by
        creating 200 block bootstrap-replicate datasets (BS) and refitting each
        modelto these datasets (see Section~\ref{sec:bootstrap-CIs}). Standard
        deviations for each inferred parameter were computed from these 200
        model fits. Parameters are as labeled and described in the above
        tables. Blank standard errors indicate that parameter was not relevant
        to the given model.
    }
    \centering
    \begin{tabular}[t]{l|cc|cc|cc|cc}
        \toprule
        & \multicolumn{2}{c|}{Single origin} & \multicolumn{2}{c|}{Cont. mig.}
        & \multicolumn{2}{c|}{Merger w/o mig.} & \multicolumn{2}{c}{Merger w/mig.} \\
        Parameter & GIM & BS & GIM & BS & GIM & BS & GIM & BS \\
        \midrule
        $N_e$ & 403 & 127 & 1777 & 951 & 326 & 406 & 1369 & 1408 \\
        $N_{MH}$ & 529 & 158 & & & & & & \\
        $N_{stem1}$ & & & 1612 & 406 & 76 & 122 & 838 & 164 \\
        $N_{stem2}$ & & & 2488 & 1001 & 1149 & 2344 & 6668 & 1154 \\
        $N_{Nama_0}$ & 370 & 79 & 2989 & 512 & 384 & 496 & 1514 & 538 \\
        $N_{Nama_F}$ & 9 & 2 & 54 & 4 & 7 & 4 & 31 & 5 \\
        $N_{MSL_0}$ & 769 & 190 & 2479 & 285 & 322 & 384 & 1165 & 421 \\
        $N_{MSL_F}$ & 606 & 185 & 6628 & 1250 & 987 & 1031 & 4332 & 1404 \\
        $N_{EA}$ & 273 & 49 & 1841 & 138 & 246 & 154 & 1628 & 252 \\
        $N_{Gumuz_F}$ & 131 & 56 & 915 & 80 & 102 & 72 & 337 & 83 \\
        $N_{EP}$ & 491 & 106 & 3246 & 168 & 408 & 177 & 1684 & 185 \\
        $N_{GBR_0}$ & 33 & 7 & 231 & 17 & 29 & 17 & 122 & 21 \\
        $N_{GBR_F}$ & 507 & 117 & 2889 & 295 & 334 & 203 & 1678 & 218 \\
        $N_{Neand}$ & 105 & 88 & 591 & 97 & 91 & 94 & 235 & 158 \\
        $T_{stems}$ & & & 391E3 & 67E3 & 27E3 & 7.6E3 & 426E3 & 284E3 \\
        $T_{stem1}$ & & & & & 20E3 & 45E3 & 166E3 & 58E3 \\
        $m_{Nama-MSL}$ & 1.6E-6 & 1.2E-6 & 3.7E-6 & 2.7E-6 & 1.1E-6 & 1.3E-6 & 4.0E-6 & 2.6E-6 \\
        $m_{Nama-EA}$ & 2.0E-6 & 1.3E-6 & 1.0E-5 & 1.8E-6 & 1.3E-6 & 1.8E-6 & 9.1E-6 & 2.8E-6 \\
        $m_{MSL-EA}$ & 7.6E-6 & 1.1E-6 & 5.3E-5 & 3.0E-6 & 5.5E-6 & 3.3E-6 & 2.6E-5 & 4.4E-6 \\
        $m_{EA-GBR}$ & 2.4E-6 & 1.1E-6 & 1.0E-5 & 1.9E-6 & 1.5E-6 & 2.2E-6 & 5.5E-6 & 2.6E-6 \\
        $m_{EA-EA}$ & 1.3E-5 & 7.5E-6 & 8.4E-5 & 1.4E-5 & 1.3E-5 & 1.4E-5 & 5.4E-5 & 1.9E-5 \\
        $f_{GBR \rightarrow EP}$ & 0.0039 & 0.0036 & 0.0037 & 0.0071 & 0.0037 & 0.0066 & 0.0075 & 0.0084 \\
        $f_{EP \rightarrow Nama}$ & 0.0039 & 0.0040 & 0.0043 & 0.0072 & 0.0042 & 0.0068 & 0.0049 & 0.0085 \\
        $f_{GBR \rightarrow Nama}$ & 0.0019 & 0.0020 & 0.0021 & 0.0030 & 0.0021 & 0.0030 & 0.0031 & 0.0035 \\
        $m_{stems}$ & & & 1.1E-5 & 7.7E-6 & & & 8.7E-5 & 2.5E-5 \\
        $m_{stem2-Nama}$ & & & 1.6E-5 & 1.1E-5 & & & & \\
        $m_{stem2-MSL}$ & & & 4.2E-5 & 1.7E-5 & & & & \\
        $m_{stem2-EA}$ & & & 9.0E-6 & 5.4E-6 & & & & \\
        $T_{Nama}$ & 2525 & 1188 & 18E3 & 6400 & 8253 & 4763 & 28E3 & 6283 \\
        $f_{stem 2 \rightarrow Nama}$ & & & & & 0.0086 & 0.017 & 0.067 & 0.018 \\
        $T_{EA}$ & & & & & 3648 & 2047 & 8865 & 4114 \\
        $f_{stem 2 \rightarrow EA}$ & & & & & 0.0074 & 0.015 & 0.059 & 0.021 \\
        $T_{MSL}$ & & & & & 570 & 1373 & 641 & 1613 \\
        $f_{stem 2 \rightarrow MSL}$ & & & & & 0.0036 & 0.0066 & 0.0085 & 0.0076 \\
        \bottomrule
    \end{tabular}
\end{table}
